A survey of HTTP caching options on the open Web

### 2015-01-08 sanity/paper1.tex
monitor to test brokenness
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@945 43ef1190-90fd-4dd7-a769-d0121f02b80e
heuristics 1
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@949 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

@@

>>>>

We next consider the simple heuristic freshness lifetime. This is
implemented as suggested in RFC7234, section~4.2.2. This is based on a
fraction of the time lapsed between the current time and the
modification time given in the \httph{Last-Modified} header. This
approach therefore still requires the Web server to be cooperative to
be successful, but commonly, Web servers can track this, based e.g. on
the file modification time of the underlying file system.

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In Figure\todo{add all
  heuristics figure}, we see that the distribution of lifetimes are
radically different from the case in Figure\todo{ref fig:allhard}. In
this case, we may cache many resources for months. Only a handful of
resources had changed in the last minutes. Since this is based
on actual times since last modifications, this suggests that many
resources should have had explicit cache headers with very long
lifetimes. \todo{compare Jürgen and LD observatory}

Moreover, by inspecting Figure\todo{add heuristic table figure}, we
note that the difference between different types of resources is much
smaller. This is confirmed by a $\chi^2$ test that yields \pvalue =
0.02.

We find that only one SPARQL Endpoint yields a heuristic lifetime, on
closer inspection, we find this to be hosted by Dydra\todo{ref?}. We
speculate that this is due to that few underlying DBMS systems help
track modification times in a way that can be used on a SPARQL result
basis.

@@

Monitor the change frequency and use a contingency table to assess the
correctness of caching headers.

@@

\todo{ref kasei on mtime}.
